To do list for this paper

### 2017-08-16 PaperToDo.Rmd
add todo

- [ ] Write an abstract - Gelman method/sanity check. First sentence of every paragraph of the intro & the very last sentence of intro. 
- [ ] Submit to journal
- [X] Spacing around figures WAY to large above/below captions - change fig.height for coord_fixed figures 
- [X] Make axes labels and text larger in figures
- [X] Make labels of points larger

>>>>

- [ ] Write an abstract - Gelman method/sanity check. First sentence of every paragraph of the intro & the very last sentence of intro. 
- [ ] Submit to journal
- [X] Spacing around figures WAY to large above/below captions - change fig.height for coord_fixed figures 
- [X] Make axes labels and text larger in figures
- [X] Make labels of points larger
- [ ] Reverse order of x-y axes on adjmat vizs
